### 2018-03-29 latex/sc18/experiments.tex
committing to sync experiments

\subsubsection{Dynamic Functional Connectivity (dFC)}

>>>>

\subsubsection{Dynamic Functional Connectivity (dFC)}
We also consider dynamic functional connectivity datasets that are generated from fMRI images of human brains.
Given a 4D fMRI data set of voxel measurements across multiple timesteps, voxels containing brain data are partitioned into a set of ZZ regions of interest (specified using domain-specific knowledge), and a single time-series signal is aggregated for each region of interest.
For each time point and pair of regions,
